Validity of a model for a cantilever two-dimensional beam

### 2024-04-07 article.tex
changes
Section capital

	\subsection*{Eigenvalue problem}
	The derivation and form of the eigenvalue problem for the three-dimensional elastic body is similar to the two-dimensional model given in section \ref{2dFEM_EP}.

@@

\end{document}

>>>>

	\subsection*{Eigenvalue problem}
	The derivation and form of the eigenvalue problem for the three-dimensional elastic body is similar to the two-dimensional model given in Section \ref{2dFEM_EP}.

@@

\end{document}`'

### 2024-04-07 article_old.tex
Section capital

Using this notation, the boundary conditions are similar to the two-dimensional model in section \ref{sssec:2D_Model:RefConf}, where the body is clamped rigidly at $\Sigma$, and free-hanging on the other sides denoted by $\Gamma$.

\subsubsection{Cantilever elastic body}
Consider a three-dimensional elastic body with rectangular cross-section, rigidly clamped to a surface at attached at the side $\Sigma$ and free-hanging at all the other sides. This is Problem 3D in section \ref{ssec:3D_Model:ModelProblems}.

@@

In section \ref{ssec:3D_Model:VariationalForm}, the variational problem for the three-dimensional cantilever model is defined by Problem 3DV. This general form can now be rewritten as in a model specific form using the reference configuration. For convenience, some of the results from section \ref{sec:3D_Model} are repeated here.

@@

\subsection{Galerkin approximation}
As mentioned in the previous section, section \ref{2d_FEM_G}, the body $\Omega$ needs to be descritised. For this is three-dimensional body, three-dimensional elements shapes are required. The elements used in this dissertation are rectangular prismatic elements. These elements are also known as `brick-shaped' elements and is described in \cite{Wu06}. This shape of element is a natural choice for a three-dimensional elastic body with a rectangular cross-section.

@@

For the this three-dimensional model, piecewise Hermite tri-cubic basis functions are used. Although this is more complex than using piecwise tri-linear basis functions, as mentioned in section \ref{2d_FEM_G}, the tri-cubic basis functions ensure faster convergence and also the derivatives of the solutions.

@@

\subsection{Eigenvalue problem}
The derivation and form of the eigenvalue problem for the three-dimensional elastic body is similar to the two-dimensional model given in section \ref{2dFEM_EP}.

@@

\subsubsection{Cantilever elastic body}
Consider a two-dimensional elastic body clamped rigidly to a surface at $x_1 = 0$. The body is free-hanging on the other boundaries. This is Problem 2D in section \ref{ssec:2D_Model:ModelProblem}.

@@

In section \ref{ssec:2D_Model:VariationalForm} the variational problem for the two dimensional cantilever model is derived and refered to as Problem 2DV. Some of the results from section \ref{sec:2D_Model} are repeated here for convenience. Using the reference configuration, these results are rewritten from a general form to a model specific form.

@@

In section \ref{sec:validity-of-a-cantilever-timoshenko-beam}, the article \cite{LVV09} was discussed. In this article, the authors investigated the validity of a cantilever Timoshenko beam by comparing it to a cantilever two-dimensional beam. In this section, the article is extended and the validity of the cantilever two-dimensional model is investigated.

@@

\subsection{The models}
The two-dimensional model is the same model as used in the previous section, Problem T-2 defined in section \ref{ssec:2D_Model:ModelProblem}. From section \ref{ssec:3D_Model:ModelProblems}, the cantilever three-dimensional model, referred to as Problem 3D.

@@

\subsection{Calculating the eigenvalues}
In section \ref{sec:FEM:3D}, the Finite Element Method for the three-dimensional beam is derived. Similar to the two-dimensional case in \ref{sec:validity-of-a-cantilever-timoshenko-beam}, the Finite Element Method is used to calculate the eigenvalues of the three-dimensional beam. The eigenvalue problem for both models have the same form, but different matrices.

\subsubsection{Problem 2DE and 3D-1E}
Find a real number $\lambda$ and a function $\bar{u} \in S^h$ such that
\begin{eqnarray}
	K\bar{u} & = & M\lambda{\bar{u}},
\end{eqnarray} where $K$ and $M$ are the standard Finite Element Method matrices defined in section \ref{ssec:2DFEM:DE} for the Problem 2DE and section \ref{3d_fem_g} for Problem 3DE.

@@

For the three-dimensional model, obtaining this level of accuracy can be difficult and computationally expensive. For the two-dimensional beam in section \ref{sec:validity-of-a-cantilever-timoshenko-beam} and the upcoming two-dimensional plate model in section \ref{sec:validity-of-a-plate} it is easier to get 5 significant digits of accuracy.

\subsection{Comparing the mode shapes}
To be able to compare the eigenvalues, the mode shapes of the two models are compared to match up the eigenvalues of the two models. This is the same approach as in section \ref{sec:validity-of-a-cantilever-timoshenko-beam}.

As seen in section \ref{sec:validity-of-a-cantilever-timoshenko-beam}, the two-dimensional model as eigenvalues and eigenvectors that are not related to beam type problems. This is also true for the three-dimensional model, and it has even more non-beam type eigenvalues.

@@

For $h$, the values used in section \ref{sec:validity-of-a-cantilever-timoshenko-beam} will be used. These values covers a range of beam shapes from a short thick beam, to a long slender beam. two cases are selected that represents realistic cases. For a short and thick beam, consider $h = 1/5$ and for a long and slender beam, consider $h = 1/20$.

>>>>

Using this notation, the boundary conditions are similar to the two-dimensional model in Section \ref{sssec:2D_Model:RefConf}, where the body is clamped rigidly at $\Sigma$, and free-hanging on the other sides denoted by $\Gamma$.

\subsubsection{Cantilever elastic body}
Consider a three-dimensional elastic body with rectangular cross-section, rigidly clamped to a surface at attached at the side $\Sigma$ and free-hanging at all the other sides. This is Problem 3D in Section \ref{ssec:3D_Model:ModelProblems}.

@@

In Section \ref{ssec:3D_Model:VariationalForm}, the variational problem for the three-dimensional cantilever model is defined by Problem 3DV. This general form can now be rewritten as in a model specific form using the reference configuration. For convenience, some of the results from Section \ref{sec:3D_Model} are repeated here.

@@

\subsection{Galerkin approximation}
As mentioned in the previous section, Section \ref{2d_FEM_G}, the body $\Omega$ needs to be descritised. For this is three-dimensional body, three-dimensional elements shapes are required. The elements used in this dissertation are rectangular prismatic elements. These elements are also known as `brick-shaped' elements and is described in \cite{Wu06}. This shape of element is a natural choice for a three-dimensional elastic body with a rectangular cross-section.

@@

For the this three-dimensional model, piecewise Hermite tri-cubic basis functions are used. Although this is more complex than using piecwise tri-linear basis functions, as mentioned in Section \ref{2d_FEM_G}, the tri-cubic basis functions ensure faster convergence and also the derivatives of the solutions.

@@

\subsection{Eigenvalue problem}
The derivation and form of the eigenvalue problem for the three-dimensional elastic body is similar to the two-dimensional model given in Section \ref{2dFEM_EP}.

@@

\subsubsection{Cantilever elastic body}
Consider a two-dimensional elastic body clamped rigidly to a surface at $x_1 = 0$. The body is free-hanging on the other boundaries. This is Problem 2D in Section \ref{ssec:2D_Model:ModelProblem}.

@@

In Section \ref{ssec:2D_Model:VariationalForm} the variational problem for the two dimensional cantilever model is derived and refered to as Problem 2DV. Some of the results from Section \ref{sec:2D_Model} are repeated here for convenience. Using the reference configuration, these results are rewritten from a general form to a model specific form.

@@

In Section \ref{sec:validity-of-a-cantilever-timoshenko-beam}, the article \cite{LVV09} was discussed. In this article, the authors investigated the validity of a cantilever Timoshenko beam by comparing it to a cantilever two-dimensional beam. In this section, the article is extended and the validity of the cantilever two-dimensional model is investigated.

@@

\subsection{The models}
The two-dimensional model is the same model as used in the previous section, Problem T-2 defined in Section \ref{ssec:2D_Model:ModelProblem}. From Section \ref{ssec:3D_Model:ModelProblems}, the cantilever three-dimensional model, referred to as Problem 3D.

@@

\subsection{Calculating the eigenvalues}
In Section \ref{sec:FEM:3D}, the Finite Element Method for the three-dimensional beam is derived. Similar to the two-dimensional case in \ref{sec:validity-of-a-cantilever-timoshenko-beam}, the Finite Element Method is used to calculate the eigenvalues of the three-dimensional beam. The eigenvalue problem for both models have the same form, but different matrices.

\subsubsection{Problem 2DE and 3D-1E}
Find a real number $\lambda$ and a function $\bar{u} \in S^h$ such that
\begin{eqnarray}
	K\bar{u} & = & M\lambda{\bar{u}},
\end{eqnarray} where $K$ and $M$ are the standard Finite Element Method matrices defined in Section \ref{ssec:2DFEM:DE} for the Problem 2DE and Section \ref{3d_fem_g} for Problem 3DE.

@@

For the three-dimensional model, obtaining this level of accuracy can be difficult and computationally expensive. For the two-dimensional beam in Section \ref{sec:validity-of-a-cantilever-timoshenko-beam} and the upcoming two-dimensional plate model in Section \ref{sec:validity-of-a-plate} it is easier to get 5 significant digits of accuracy.

\subsection{Comparing the mode shapes}
To be able to compare the eigenvalues, the mode shapes of the two models are compared to match up the eigenvalues of the two models. This is the same approach as in Section \ref{sec:validity-of-a-cantilever-timoshenko-beam}.

As seen in Section \ref{sec:validity-of-a-cantilever-timoshenko-beam}, the two-dimensional model as eigenvalues and eigenvectors that are not related to beam type problems. This is also true for the three-dimensional model, and it has even more non-beam type eigenvalues.

@@

For $h$, the values used in Section \ref{sec:validity-of-a-cantilever-timoshenko-beam} will be used. These values covers a range of beam shapes from a short thick beam, to a long slender beam. two cases are selected that represents realistic cases. For a short and thick beam, consider $h = 1/5$ and for a long and slender beam, consider $h = 1/20$.

### 2024-04-07 files/Chapter1/1DModel.tex
Section capital

    \subsubsection*{Dimensionless form}\label{sssec:1D_Model:DimensionlessForm}
    As mentioned in Subsection \ref{ssec:3D_Model:DimensionlessForm}, the same dimensionless scaling is used for all the models in this dissertation.\\

@@

    Choose $t_0$ the same as in Subsection \ref{ssec:3D_Model:DimensionlessForm}, i.e. \[t_0 = \ell\sqrt{\frac{\rho}{G\kappa^2}}.\]

@@

    Interestingly, it turns out that
    \begin{eqnarray*}
        \frac{\beta}{\alpha} & = & \gamma
    \end{eqnarray*} where $\gamma$ is the dimensionless parameter defined in Subsection \ref{ssec:3D_Model:DimensionlessForm}.\\

    \textbf{Remark} Recall that in Subsection \ref{ssec:3D_Model:DimensionlessForm} the constant $G\kappa^2$ was used for the scaling of the stresses.

>>>>

    \subsubsection*{Dimensionless form}\label{sssec:1D_Model:DimensionlessForm}
    As mentioned in SubSection \ref{ssec:3D_Model:DimensionlessForm}, the same dimensionless scaling is used for all the models in this dissertation.\\

@@

    Choose $t_0$ the same as in SubSection \ref{ssec:3D_Model:DimensionlessForm}, i.e. \[t_0 = \ell\sqrt{\frac{\rho}{G\kappa^2}}.\]

@@

    Interestingly, it turns out that
    \begin{eqnarray*}
        \frac{\beta}{\alpha} & = & \gamma
    \end{eqnarray*} where $\gamma$ is the dimensionless parameter defined in SubSection \ref{ssec:3D_Model:DimensionlessForm}.\\

    \textbf{Remark} Recall that in SubSection \ref{ssec:3D_Model:DimensionlessForm} the constant $G\kappa^2$ was used for the scaling of the stresses.

### 2024-04-07 files/Chapter1/3DModel.tex
Section capital

\documentclass[../../main.tex]{subfiles}
\begin{document}
\section{Model problem for a three-dimensional elastic solid} \label{sec:3D_Model}
In this section we introduces the linear theory for a three-dimensional elastic
solid. The textbook of Fung \cite{Fung65} is used with some changes in the
notation. \\

The equation of motion and constitutive equation are given in subsection
\ref{ssec:3D_Model:EquationOfMotion}. The dimensionless form of the equation of
motion and constitutive equation are derived in subsection
\ref{ssec:3D_Model:DimensionlessForm}. Model problems are presented in
subsection \ref{ssec:3D_Model:ModelProblems}. The variational form for the
vibration problem is given in section \ref{ssec:3D_Model:VariationalForm}.
Plane stress is discussed in section \ref{ssec:3D_Model:PlaneStress}

@@

\subsubsection*{Strain}\label{sssec:3D_Model:Strain}
Infinitesimal strain tensor is defined on $\Omega$ as $\mathcal{E}$\label{sym:mathcalE}, with components
\begin{eqnarray}
	\varepsilon_{ij} = \frac{1}{2}\left( \frac{\partial u_i}{\partial x_j} + \frac{\partial u_j}{\partial x_i} \right). \label{eq:3D_Model:Strain}
\end{eqnarray}\label{sym:varepsilonij}

@@

\subsubsection*{Hooke's law in the alternative form}\label{sssec:3D_Model:Hooke'sLaw2}
If the principal stresses $\sigma_i$ are all non-zero, then Hooke's law can be written in the following form
\begin{eqnarray}
	T = \left( \frac{E}{1+\nu} \right)\mathcal{E} + \frac{\nu E}{(1+\nu)(1-2\nu)}\textrm{Tr}(\mathcal{E})I \label{eq:3D_Model:CE}.
\end{eqnarray}
$\textrm{Tr}(\mathcal{E}) = \epsilon_{11} + \epsilon_{12} + \epsilon_{13}$ is the trace of the strain operator $\mathcal{E}$.\\

@@

\subsection{Dimensionless form} \label{ssec:3D_Model:DimensionlessForm}
The dimensionless form of the equation of motion and constitutive equation are
derived in this subsection. Suppose $\ell$ represents some notable dimension
(e.g.the length) of the elastic body and $G$ the shear modulus of elasticity.\\

@@

where $\kappa^2$ is a dimensionless constant and $t_0$ must be specified. A
convenient choice for $t_0$ (see section \ref{sec:1D_Model}) is \[t_0 = \ell\sqrt{\frac{\rho}{G\kappa^2}}.\]

Substitution into \eqref{eq:3D_Model:EM} and yields
\begin{eqnarray*}
	\partial_{\tau} u^{*} = \textrm{div}T^* + Q^*.
\end{eqnarray*}
where $T^* = \sigma_{i,j}^*(\xi,\tau)$.\\

The dimensionless form of \eqref{eq:3D_Model:HL} and \eqref{eq:3D_Model:CE} are
\begin{eqnarray*}
	\mathcal{E} = \frac{G \kappa^2}{E} \left[ (1+\nu)T^* - \nu \textrm{Tr}(T^*)I \right]
\end{eqnarray*}\label{sym:I}

and
\begin{eqnarray*}
	T^* = \frac{E}{G \kappa^2} \left[\left( \frac{1}{1+\nu} \right)\mathcal{E} + \frac{\nu}{(1+\nu)(1-2\nu)}\textrm{Tr}(\mathcal{E})I \right]
\end{eqnarray*}

@@

Using this dimensionless constant,
\begin{eqnarray}
	\mathcal{E} = \gamma(1+\nu)T^* - \gamma\nu \textrm{Tr}(T^*)I \label{DM_H_E}
\end{eqnarray}
and
\begin{eqnarray}
	T^* = \frac{1}{\gamma(1+\nu)}\mathcal{E} + \frac{\nu}{\gamma(1+\nu)(1-2\nu)}\textrm{Tr}(\mathcal{E})I. \label{DM_H_T}
\end{eqnarray}

\textbf{Remark} The constant $G\kappa^2$ is introduced to allow for comparisons of the models in later chapters. The constant comes from the Timoshenko beam theory and is explained in section \ref{sec:1D_Model} \\

In the rest of section 1.2 the original notation is retained for convenience.

@@

\subsubsection*{Constitutive equations in dimensionless form}\label{sssec:3D_Model:ConstitutiveEquationsDimensionless}
\begin{eqnarray}
	T = \frac{1}{\gamma(1+\nu)} \mathcal{E} + \frac{\nu}{\gamma(1+\nu)(1-2\nu)}\textrm{Tr}(\mathcal{E})I \label{eq:3D_Model:CE-D}
\end{eqnarray}

\subsection{Model problems}\label{ssec:3D_Model:ModelProblems}
Suppose $\Omega \subset R^3$ is the reference configuration for a solid
executing small vibrations. The boundary of $\Omega$ can be divided into two
distinct parts, referred to as $\Sigma$ and $\Gamma$. The following will be
considered a model problem for a three-dimensional elastic body.
\begin{enumerate}
	\item[] The equations of motion \eqref{eq:3D_Model:EM-D} and \eqref{eq:3D_Model:divT-D} is satisfied in $\Omega$;
	\item[] Hooke's law \eqref{eq:3D_Model:CE-D} is satisfied in $\Omega$;
	\item[] The displacement $u = u_\Sigma$ is specified on
		$\Sigma$;
	\item[] The traction $Tn = t_\Gamma$ is specified on
		$\Gamma$.
\end{enumerate} \label{sym:n}\label{sym:SigmaGamma}

@@

Boundary Conditions:
\begin{eqnarray*}
	u & = & 0 \quad \textrm{ on } \Sigma\\
	Tn & = & 0 \quad \textrm{ on } \Gamma
\end{eqnarray*} With $n$ the outward normal vector to $\Omega$.

@@

Boundary Conditions:
\begin{eqnarray*}
	Tn & = & 0 \quad \textrm{ on } \partial\Omega
\end{eqnarray*} With $n$ the unit outward normal vector. \label{sym:boundaryOmega}

\subsection{Variational form}\label{ssec:3D_Model:VariationalForm}
Let $\phi \in C({\Omega})$ be an arbitrary vector valued function. Multiplying
$\phi$ to equation \eqref{eq:3D_Model:EM-D} and integrating over the domain
$\Omega$ results in, \label{sym:Cn} \label{sym:phi}

@@

\subsubsection{Problem 3D-1V}\label{sssec:3D_Model:Problem3D1V}
Find a function $u$ such that for all $t>0$, $u \in T(\Omega)$ and
\begin{align}
	c(u,\phi) = -b(u,\phi) + (Q,\phi), \label{eq:3D_Model:Problem3D1VEq}
\end{align}\label{sym:c}
for all $\phi \in T(\Omega)$\\

The well-posedness of the model is treated in Chapter 2, where Korn's
inequality is presented. Applications are continued in Chapter 4, 5 and 6. In
Chapter 4, a free-free three-dimensional beam is discussed as part of an
empirical study. In Chapter 5, the finite element analysis is applied to a
cantilever beam to solve the eigenvalue problem. In Chapter 6, a cantilever
beam in used in the comparison of our linear models.

@@

\noindent
\begin{minipage}{.5\linewidth}
	\begin{eqnarray*}
		\sigma_{11} & = & \frac{1}{\gamma(1-\nu^2)} ( \varepsilon_{11} + \nu\varepsilon_{22})\\
		\sigma_{22} & = & \frac{1}{\gamma(1-\nu^2)} (\nu \varepsilon_{11} + \varepsilon_{22}).
	\end{eqnarray*}
\end{minipage}%
\begin{minipage}{.5\linewidth}
	\begin{eqnarray}
		\sigma_{12} & = & \frac{1}{\gamma(1+\nu)} \varepsilon_{12} \label{stress_comp}
	\end{eqnarray}
\end{minipage}\\

@@

This is known as general plane stress. In this dissertation only a special case
of general plane stress is considered in section \ref{sec:2D_Model}.

>>>>

\documentclass[../../main.tex]{subfiles}ite{VS18}
\begin{document}
\section{Model problem for a three-dimensional elastic solid} \label{sec:3D_Model}
In this section we introduce the linear theory for a three-dimensional elastic
solid. The textbook of Fung \cite{Fung65} is used with some changes in the
notation. \\

The equation of motion and constitutive equation are given in Subsection
\ref{ssec:3D_Model:EquationOfMotion}. The dimensionless form of the equation of
motion and constitutive equation are derived in Subsection
\ref{ssec:3D_Model:DimensionlessForm}. Model problems are presented in
SubSection \ref{ssec:3D_Model:ModelProblems}. The variational form for the
vibration problem is given in Section \ref{ssec:3D_Model:VariationalForm}.
Plane stress is discussed in Section \ref{ssec:3D_Model:PlaneStress}

@@

\subsubsection*{Strain}\label{sssec:3D_Model:Strain}
The infinitesimal strain tensor is defined on $\Omega$ as $\mathcal{E}$\label{sym:mathcalE}, with components
\begin{eqnarray}
	\varepsilon_{ij} = \frac{1}{2}\left( \frac{\partial u_i}{\partial x_j} + \frac{\partial u_j}{\partial x_i} \right). \label{eq:3D_Model:Strain}
\end{eqnarray}\label{sym:varepsilonij}

@@

\subsubsection*{Hooke's law in the alternative form}\label{sssec:3D_Model:Hooke'sLaw2}
If the principal stresses $\sigma_i$ are all non-zero, then Hooke's law can be written in the following form
\begin{eqnarray}
	T = \left( \frac{E}{1+\nu} \right)\mathcal{E} + \frac{\nu E}{(1+\nu)(1-2\nu)}\textrm{Tr}(\mathcal{E})I \label{eq:3D_Model:CE}.
\end{eqnarray}
$\textrm{Tr}(\mathcal{E}) = \varepsilon_{11} + \varepsilon_{12} + \varepsilon_{13}$ is the trace of the strain operator $\mathcal{E}$.\\

@@

\subsection{Dimensionless form} \label{ssec:3D_Model:DimensionlessForm}
The dimensionless form of the equation of motion and constitutive equation are
derived in this subsection. Suppose $\ell$ represents some notable dimension
(e.g. the length) of the elastic body and $G$ the shear modulus of elasticity.\\

@@

where $\kappa^2$ is a dimensionless constant and $t_0$ must be specified. A
convenient choice for $t_0$ (see Section \ref{sec:1D_Model}) is \[t_0 = \ell\sqrt{\frac{\rho}{G\kappa^2}}.\]

Substitution into \eqref{eq:3D_Model:EM} yields
\begin{eqnarray*}
	\partial_{\tau} u^{*} = \textrm{div}T^* + Q^*,
\end{eqnarray*}
where $T^* = \sigma_{i,j}^*(\xi,\tau)$.

The dimensionless form of \eqref{eq:3D_Model:HL} and \eqref{eq:3D_Model:CE} are
\begin{eqnarray}
	\mathcal{E} = \frac{G \kappa^2}{E} \left[ (1+\nu)T^* - \nu \textrm{Tr}(T^*)I \right] \label{sym:E_2}
\end{eqnarray}\label{sym:I}
and
\begin{eqnarray}
	T^* = \frac{E}{G \kappa^2} \left[\left( \frac{1}{1+\nu} \right)\mathcal{E} + \frac{\nu}{(1+\nu)(1-2\nu)}\textrm{Tr}(\mathcal{E})I \right]. \label{sym:T_2}
\end{eqnarray}

@@

Using this dimensionless constant, \eqref{sym:E_2} and \eqref{sym:T_2} becomes
\begin{eqnarray}
	\mathcal{E} = \gamma(1+\nu)T^* - \gamma\nu \textrm{Tr}(T^*)I \label{DM_H_E}
\end{eqnarray}
and
\begin{eqnarray}
	T^* = \frac{1}{\gamma(1+\nu)}\mathcal{E} + \frac{\nu}{\gamma(1+\nu)(1-2\nu)}\textrm{Tr}(\mathcal{E})I. \label{DM_H_T}
\end{eqnarray}

\textbf{Remark} The constant $G\kappa^2$ is introduced to allow for comparisons of the models in later chapters. The constant comes from the Timoshenko beam theory and is explained in Section \ref{sec:1D_Model} \\

In the rest of Section 1.2 the original notation is retained for convenience.

@@

\subsubsection*{Constitutive equation in dimensionless form}\label{sssec:3D_Model:ConstitutiveEquationsDimensionless}
\begin{eqnarray}
	T = \frac{1}{\gamma(1+\nu)} \mathcal{E} + \frac{\nu}{\gamma(1+\nu)(1-2\nu)}\textrm{Tr}(\mathcal{E})I \label{eq:3D_Model:CE-D}
\end{eqnarray}

\subsection{Model problems}\label{ssec:3D_Model:ModelProblems}
Suppose $\Omega \subset R^3$ is the reference configuration for a solid
executing small vibrations. The boundary of $\Omega$ can be divided into two
distinct parts, referred to as $\Sigma$ and $\Gamma$. The following will be
considered a model problem for a three-dimensional elastic body.
\begin{enumerate}
	\item[] The equations of motion \eqref{eq:3D_Model:EM-D} and \eqref{eq:3D_Model:divT-D} are satisfied in $\Omega$;
	\item[] Hooke's law \eqref{eq:3D_Model:CE-D} is satisfied in $\Omega$;
	\item[] The displacement $u = u_\Sigma$ is specified on
		$\Sigma$;
	\item[] The traction $Tn = t_\Gamma$ is specified on
		$\Gamma$.
\end{enumerate} \label{sym:n}\label{sym:SigmaGamma}

@@

\begin{eqnarray*}
	u & = & 0 \quad \textrm{ on } \Sigma\\
	Tn & = & 0 \quad \textrm{ on } \Gamma
\end{eqnarray*} with $n$ the outward normal vector to $\Omega$.

@@

\begin{eqnarray*}
	Tn & = & 0 \quad \textrm{ on } \partial\Omega
\end{eqnarray*} with $n$ the unit outward normal vector. \label{sym:boundaryOmega}

\subsection{Variational form}\label{ssec:3D_Model:VariationalForm}
Let $\phi \in C({\Omega})$ be an arbitrary vector valued function. Multiplying
$\phi$ with equation \eqref{eq:3D_Model:EM-D} and integrating over the domain
$\Omega$ results in, \label{sym:Cn} \label{sym:phi}

@@

\subsubsection{Problem 3D-1V}\label{sssec:3D_Model:Problem3D1V}
Find a function $u$ such that for all $t>0$, $u \in T(\Omega)$ and
\begin{align}
	c(u,\phi) = -b(u,\phi) + (Q,\phi), \label{eq:3D_Model:Problem3D1VEq}
\end{align}\label{sym:c}
for all $\phi \in T(\Omega)$.\\

The well-posedness of the model is treated in Chapter 2, where Korn's
inequality is presented. Applications are continued in Chapters 4, 5 and 6. In
Chapter 4, a free-free three-dimensional beam is discussed as part of an
empirical study. In Chapter 5, the finite element analysis is applied to a
cantilever beam to solve the eigenvalue problem. In Chapter 6, a cantilever
beam is used in the comparison of the linear models.

@@

\noindent
\begin{minipage}{.5\linewidth}
	\begin{eqnarray*}
		\sigma_{11} & = & \frac{1}{\gamma(1-\nu^2)} ( \varepsilon_{11} + \nu\varepsilon_{22}),\\
		\sigma_{22} & = & \frac{1}{\gamma(1-\nu^2)} (\nu \varepsilon_{11} + \varepsilon_{22}).
	\end{eqnarray*}
\end{minipage}%
\begin{minipage}{.5\linewidth}
	\begin{eqnarray}
		\sigma_{12} & = & \frac{1}{\gamma(1+\nu)} \varepsilon_{12}, \label{stress_comp}
	\end{eqnarray}
\end{minipage}\\

@@

This is known as general plane stress. In this dissertation only a special case
of general plane stress is considered in Section \ref{sec:2D_Model}.

### 2024-04-07 files/Chapter4/CantileverBeam.tex
Section capital

\documentclass[../../main.tex]{subfiles}
\begin{document}
\section{Cantilever beam} \label{sec:Timo:Cantilever}
Consider a cantilever Timoshenko beam model (Problem T-3 as defined in section \ref{ssec:1D_Model:ModelProblems}). The eigenvalue problem of Problem T-3 is denoted by Problem T-3E. This section serves as an example of the application of the theory from \cite{VV06}.\\

>>>>

\documentclass[../../main.tex]{subfiles}
\begin{document}
\section{Cantilever beam} \label{sec:Timo:Cantilever}
Consider a cantilever Timoshenko beam model (Problem T-3 as defined in Section \ref{ssec:1D_Model:ModelProblems}). The eigenvalue problem of Problem T-3 is denoted by Problem T-3E. This section serves as an example of the application of the theory from \cite{VV06}.\\

### 2024-04-07 files/Chapter4/CantileverTimo.tex
Section capital

\subsection{The model problem}
Consider the dimensionless equations of motion \ref{eq:1D_Model:EquationOfMotion1D} and \ref{eq:1D_Model:EquationOfMotion2D} and constitutive equations \ref{eq:1D_Model:ConstitutiveEquations1D} and \ref{eq:1D_Model:ConstitutiveEquations2D} of a Timoshenko beam, as given in section \ref{sec:1D_Model}. The model in [DBVXX] adds two damping terms to these equations.

>>>>

\subsection{The model problem}
Consider the dimensionless equations of motion \ref{eq:1D_Model:EquationOfMotion1D} and \ref{eq:1D_Model:EquationOfMotion2D} and constitutive equations \ref{eq:1D_Model:ConstitutiveEquations1D} and \ref{eq:1D_Model:ConstitutiveEquations2D} of a Timoshenko beam, as given in Section \ref{sec:1D_Model}. The model in [DBVXX] adds two damping terms to these equations.

### 2024-04-07 files/Chapter4/FreeFreeTimo.tex
Section capital

\documentclass[../../main.tex]{subfiles}
\begin{document}
\section{Free-free Timoshenko beam}\label{sec:Timo:Free}
Consider a free-free Timoshenko beam model (Problem T-4 in section \ref{ssec:1D_Model:ModelProblems}).The eigenvalue problem of Problem T-4 is denoted by Problem T-4E. Similar to the previous section, this section serves as an example of the application of the theory from [VV02].\\

>>>>

\documentclass[../../main.tex]{subfiles}
\begin{document}
\section{Free-free Timoshenko beam}\label{sec:Timo:Free}
Consider a free-free Timoshenko beam model (Problem T-4 in Section \ref{ssec:1D_Model:ModelProblems}).The eigenvalue problem of Problem T-4 is denoted by Problem T-4E. Similar to the previous section, this section serves as an example of the application of the theory from [VV02].\\

### 2024-04-07 files/Chapter4/ModalAnalysisTimo.tex
Section capital

\documentclass[../../main.tex]{subfiles}
\begin{document}
\section{Introduction}
An example of modal analysis of a Timoshenko beam is given in section \ref{sec:existence:ModalAnalysis}. In this chapter, more general theory for modal analysis of the Timoshenko beam theory is discussed, as well as more examples of the application of the theory.

@@

Recall from section \ref{sec:1D_Model}, $u$ represents the transverse motion of the beam, $\phi$ is the angle of rotation of the cross-section of the beam, $\alpha$ and $\gamma$ are dimensionless constants defined in section 1.5 and $\lambda$ represents the eigenvalue.

@@

The authors of \cite{VV06} provide a detailed example of the application of the above strategy for determining the eigenvalues and eigenvectors. The example used is a pinned-pinned beam, the same model as in section \ref{subsec:Timoshenko_Modal_Analsis}.

@@

A rigourous proof of the above results can be found in \cite{VV06}. These results also prove the Theorem 1 presented in section \ref{subsec:Timoshenko_Modal_Analsis}.

>>>>

\documentclass[../../main.tex]{subfiles}
\begin{document}
\section{Introduction}
An example of modal analysis of a Timoshenko beam is given in Section \ref{sec:existence:ModalAnalysis}. In this chapter, more general theory for modal analysis of the Timoshenko beam theory is discussed, as well as more examples of the application of the theory.

@@

Recall from Section \ref{sec:1D_Model}, $u$ represents the transverse motion of the beam, $\phi$ is the angle of rotation of the cross-section of the beam, $\alpha$ and $\gamma$ are dimensionless constants defined in section 1.5 and $\lambda$ represents the eigenvalue.

@@

The authors of \cite{VV06} provide a detailed example of the application of the above strategy for determining the eigenvalues and eigenvectors. The example used is a pinned-pinned beam, the same model as in Section \ref{subsec:Timoshenko_Modal_Analsis}.

@@

A rigourous proof of the above results can be found in \cite{VV06}. These results also prove the Theorem 1 presented in Section \ref{subsec:Timoshenko_Modal_Analsis}.

### 2024-04-07 files/Chapter4/SP06.tex
Section capital

\subsection{Mathematical models}
Let $\Omega$ be the reference configuration of a free-free beam with square cross-section. The authors of \cite{SP06} do not formulate the models in the article. Consider Problem T-4 from section \ref{ssec:1D_Model:ModelProblems} for the free-free Timoshenko beam and Problem 3D-2 from section \ref{ssec:3D_Model:ModelProblems} for the free-free three-dimensional beam. The boundary conditions and reference configurations of the model problems are given below.

@@

\textcolor{red}{Onseker oor die***************}\\
In [LC81], a single frequency equation for the free-free beam is given. From the work in section \ref{sec:Timo:EigenvalueProblem}, it has been shown that there can be up to three-different frequency equations depending on $\alpha$. As the $\alpha$ for this beam is very small, the eigenvalues 9 and above will not be considered in this dissertation.\\
\textcolor{red}{Onseker oor die***************}

>>>>

\subsection{Mathematical models}
Let $\Omega$ be the reference configuration of a free-free beam with square cross-section. The authors of \cite{SP06} do not formulate the models in the article. Consider Problem T-4 from Section \ref{ssec:1D_Model:ModelProblems} for the free-free Timoshenko beam and Problem 3D-2 from Section \ref{ssec:3D_Model:ModelProblems} for the free-free three-dimensional beam. The boundary conditions and reference configurations of the model problems are given below.

@@

\textcolor{red}{Onseker oor die***************}\\
In [LC81], a single frequency equation for the free-free beam is given. From the work in Section \ref{sec:Timo:EigenvalueProblem}, it has been shown that there can be up to three-different frequency equations depending on $\alpha$. As the $\alpha$ for this beam is very small, the eigenvalues 9 and above will not be considered in this dissertation.\\
\textcolor{red}{Onseker oor die***************}

### 2024-04-07 files/Chapter4/SuspendedBeamModel.tex
Section capital

The suspended Timoshenko beam model is referred to as Problem T-3 in this \ref{ssec:1D_Model:ModelProblems}. The beam is suspended at both endpoints by linear springs. The boundary conditions of Problem T-3 as given in section \ref{ssec:1D_Model:ModelProblems} can be rewritten by substituting the constitutive equations \eqref{eq:1D_Model:ConstitutiveEquations1D} and \eqref{eq:1D_Model:ConstitutiveEquations2D}.

>>>>

The suspended Timoshenko beam model is referred to as Problem T-3 in this \ref{ssec:1D_Model:ModelProblems}. The beam is suspended at both endpoints by linear springs. The boundary conditions of Problem T-3 as given in Section \ref{ssec:1D_Model:ModelProblems} can be rewritten by substituting the constitutive equations \eqref{eq:1D_Model:ConstitutiveEquations1D} and \eqref{eq:1D_Model:ConstitutiveEquations2D}.
